Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-17 ebayes_rnaseq_heterosis.tex
discussion

Through a simulation study, we demonstarted that this method outperformed alternative methods (that are not designed to detect heterosis), and performed comparably with an implementation of our model in ShrinkBayes which estimates the full posterior via INLA.

>>>>

Through a simulation study, we demonstrated that this method outperformed alternative methods (that are not designed to detect heterosis), and performed comparably with an implementation of our model in ShrinkBayes which estimates the full posterior via INLA. We then demonstrated the use of the methodology on a maize experiment where phenotypic heterosis is well known. 
% Estimates of heterosis to compare with Ji et. al.
In addition to providing estimates of heterosis probabilities and effect sizes, this real data analysis demonstrated violation of normality assumptions that suggest model improvements to improve power for detection of gene heterosis. Developing the details of such an extension is the subject of some of our ongoing and future research.
